\begin{thebibliography}{9}

\bibitem{hic} Fu, Tianjun, Ahmed Abbasi, and Hsinchun Chen. ``A hybrid approach to web forum interactional coherence analysis." Journal of the Association for Information Science and Technology 59.8 (2008): 1195-1209.

\bibitem{lin} Lin, Dekang. ``An information-theoretic definition of similarity." Icml. Vol. 98. No. 1998. 1998.

\bibitem{Bavelas-centrality} Bavelas, Alex. ``A mathematical model for group structures." Human organization 7.3 (1948): 16-30.

\bibitem{Sabidussi-centrality} Sabidussi, Gert. ``The centrality index of a graph." Psychometrika 31.4 (1966): 581-603.

\bibitem{Freeman-centrality} Freeman, Linton C. ``Centrality in social networks conceptual clarification." Social networks 1.3 (1978): 215-239.

\bibitem{Anthonisse-betweenness} Anthonisse, Jac M. ``The rush in a directed graph." Stichting Mathematisch Centrum. Mathematische Besliskunde BN 9/71 (1971).

\bibitem{Freeman-betweenness} Freeman, Linton C. ``A set of measures of centrality based on betweenness." Sociometry (1977): 35-41.

\bibitem{Brandes-betweenness} Brandes, Ulrik. ``A faster algorithm for betweenness centrality." Journal of mathematical sociology 25.2 (2001): 163-177. 

\bibitem{louvain} Blondel, Vincent D., et al. ``Fast unfolding of communities in large networks." Journal of statistical mechanics: theory and experiment 2008.10 (2008): P10008.

\bibitem{apriori} Agarwal, Rakesh, and Ramakrishnan Srikant. ``Fast algorithms for mining association rules." Proc. of the 20th VLDB Conference. 1994.

\bibitem{eclat} Zaki, Mohammed Javeed, et al. ``New Algorithms for Fast Discovery of Association Rules." KDD. Vol. 97. 1997.

\bibitem{se-tree} Rymon, Ron. ``Search through systematic set enumeration." (1992).

\end{thebibliography}
